---
title: "More Weather Inclemency, Less Shared Bike Borrowed?"
author: "Jinming Li"
description: "Final Project for 2022 Fall GOV50 in Harvard College"
output:
  distill::distill_article:
    self_contained: false
---

```{r}
options(width = 100)
library(infer)
library(tidyverse)
library(ggplot2)
library(dplyr)
```



## Introduction
Bike sharing is a transport service where bicycles provided by governments or private companies are available for public use on a rental basis. Recent years have witnessed an inflation of people's interest in bike-sharing infrastructure and investment due to its role in mitigating congestion and pollution. Compared to the traditional sharing project, the daily operation of the new generation of bike sharing relies on smartphone technology. In this, it is able to detect and record valuable information for governments, companies, and researchers, which offers insight into urban commute patterns and usage habits. By analyzing the factors that affect the number of shared bikes borrowed, city and business owners are able to understand the demand for rental bikes better, thus distributing them more responsively.

In this study, I plan to investigate to what extent inclement weathers influence the count of total rental bikes borrowed by both casual and registered users. I hypothesize that the count decreases as weather inclemency escalates. When it is sunny or cloudy, I expect that people are more likely to use and rent a bike; when it is misty, rainy, or snowy, people tends to use other vehicles that reduces their exposure to adversities like low visibility and precipitation.



## Data
This research is based on the following dataset whose sources include the system data of a bike sharing company, Washington, D.C.'s Capital Bikeshare, online weather information, and holiday schedule, showing the daily count of rental bikes between years 2011 and 2012 in the system with the corresponding weather conditions.

Fanaee-T, Hadi (2013). “Bike Sharing Dataset Data Set.” https://archive.ics.uci.edu/ml/datasets/Bike+Sharing+Dataset.

The following table shows the variables excerpted from the raw dataset. It has 6 independent variables, including `workingday`, `weathersit`, `temp`, `atemp`, `hum`, and `windspeed` and 1 dependent variable, `cnt`. Precisely, the `cnt` is a discrete variable of the total number of bikes borrowed by both casual and registered users. The `workingday` is a dichotomous variable; if the day is neither weekend nor holiday is 1, otherwise is 0. The `weathersit` is coded from 1 to 4 in accordance with the weather inclemency. The `temp` is the normalized temperature in Celsius whose values are derived via $\frac{t - t_{min}}{t_{max} - t_{min}}$. The `atemp` is the normalized feeling temperature in Celsius whose values are derived via $\frac{t - t_{min}}{t_{max} - t_{min}}$. The `hum` is the normalized humidity where the values are divided to 100. The `windspeed` is the normalized wind speed where the values are divided to 67.

This is a cross-sectional study that runs a bivariate regression of `cnt` on `weathersit` to explores the relationship between the count of rental bikes and weather inclemency and then a multivariate regression of `cnt` on all independent variables to control the confounders.

| Variable     | Description                                                                                                                        |
|---------------------|---------------------------------------------------|
| `workingday` | Indicator variable for whether day is a working day (1) or not (0). |
| `weathersit` | Indicator variable for weather inclemency, segmented as sunny or cloudy (1), mist (2), light precipitation (3), and heavy precipitation (4). |
| `temp`       | Normalized temperature in Celsius.                                                                                                 |
| `atemp`      | Normalized feeling temperature in Celsius.                                                                                         |
| `hum`        | Normalized humidity.                                                                                                               |
| `windspeed`  | Normalized wind speed.                                                                                                             |
| `cnt`        | Count of total rental bikes.                                                                  |

According to the plot (Figure 1), the distribution of the dependent variable, the daily count of rental bikes, looks approximately multimodal with one primary peak at the center of the curve around 4500 and two smaller peaks around 2000 and 7000, respectively.

```{r}
df_raw <- read.csv("day.csv")
df <- df_raw[, c(8, 9, 10, 11, 12, 13, 16)]

dist_cnt <- df |>
  ggplot(aes(x = cnt)) +
  geom_histogram() +
  labs(title = "Figure 1: Distribution of CNT",
       x = "Count of CNT",
       y = "Count")
dist_cnt
```



## Result
In the bivariate regression, the coefficient of `weathersit` is -1057.3, which means that a one-point increase in weather inclemency is associated with a decrease in count of total rental bikes of 1057.3 on average. According to the boxplot (Figure 2), as the lower quartile, median, and upper quartile get lower when the weather gets more inclement, the count of total rental bikes tends to decrease when the weather inclemency increases.

```{r}
reg_main <- lm (cnt ~ weathersit, data = df)
summary(reg_main)

df |>
  mutate(
    weather = case_when(
      weathersit == 1 ~ "Sunny or Cloudy",
      weathersit == 2 ~ "Mist",
      weathersit == 3 ~ "Light Precipitation",
      weathersit == 4 ~ "Heavy Precipitation"
    )
  ) |>
  ggplot(aes(x = weather, y = cnt)) +
  geom_boxplot() +
  labs(title = "Figure 2: Relationship Between CNT and Weather",
       x = "Weather",
       y = "CNT")
```

In the multivariate regression, the p-values of `weathersit`, `atemp`, `hum`, and `windspeed` are smaller than 0.1, so their coefficient are statistically significant at the 0.1 level.

Precisely, the coefficient of `weathersit` is -483.3, meaning that holding other variables at a fixed value, a one-point increase in weather inclemency is associated with a decrease in count of total rental bikes of 483.3 on average. The coefficient of `atemp` is 4483.3, meaning that holding other variables at a fixed value, a one-point increase in normalized feeling temperature is associated with an increase in count of total rental bikes of 4483.3 on average. The coefficient of `hum` is -1936.8, meaning that holding other variables at a fixed value, a one-point increase in normalized humidity is associated with a decrease in count of total rental bikes of 1936.8 on average. The coefficient of `windspeed` is -3963.3, meaning that holding other variables at a fixed value, a one-point increase in normalized wind speed is associated with a decrease in count of total rental bikes of 3963.3 on average.

Also, there is a change in the coefficient of `weathersit` in the two models. The size of the estimated negative effect of `weathersit` has on `cnt` decreases once `atemp`, `hum`, and `windspeed` are controlled. In other words, some of the effect weather inclemency has on the count of total rental bikes, detected in the bivariate regression, is caused by the confounding variables, which in this case are feeling temperature, humidity, and wind speed. This is intuitive because the weather inclemency are indexed in accordance with types of weather and the different types of weather are characterized by different level of those parameters; for example, an inclement rainy day has higher level of humidity and an inclement snowy day has lower feeling temperature.

It is plausible to interpret the effect of weather inclemency causally, as its confounders can be controlled.

```{r}
reg_all <- lm(cnt ~ workingday + weathersit + temp + atemp + hum + windspeed, data = df)
summary(reg_all)
```

```{r}
df |>
  ggplot(aes(x = atemp, y = cnt)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Figure 3: Regression of CNT on Feeling Temperature",
       x = "Normalized feeling temperature",
       y = "CNT")

df |>
  ggplot(aes(x = hum, y = cnt)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Figure 4: Regression of CNT on Humidity",
       x = "Normalized Humidity",
       y = "CNT")

df |>
  ggplot(aes(x = windspeed, y = cnt)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Figure 5: Regression of CNT on Wind Speed",
       x = "Normalized Wind Speed",
       y = "CNT")
```



## Conclusion
The study shows that the inclement weather has a negative impact on the count of total rental bikes borrowed and the effect decreases once we control for feeling temperature, humidity, and wind speed.

This study has several limitations. The sample includes only 731 observations, which is too small to generalize the conclusion. Plus, the independent variable of weather inclemency index is coded on a 1 to 4 scale according to the severity of different types of weather. They are categorically divided into 4 bundles in the dataset, yet the segmentation is far from perfect as the differences among bundles are not linear. Thus, the inclemency should be measured by other quantifiable parameters, which in this case can be feeling temperature, humidity, wind speed, etc. In other words, those confounders possibly mediate or moderate weather's effect on the count of total rental bikes, which is not covered by the regression model that assumes the independence of data and reveals only the observable variables and the direct effects.

To improve the study, we can utilize other models like structural equation model or multilevel models. Moreover, we can collect more data that might contribute the count of total rental bikes borrowed. Precisely, whether the service equipped with a dockless system and the number of bikes supplied in a given range might impact people's capability of renting a bike. The location also matters as the geographical features and hence people's commuting habits influence their willingness to use bikes. For example, in China, the service is much more prospect in Beijing than in Chongqing, because the former is a city built on the North China Plain with urban planning friendly to bikes, while the latter is a mountainous city with steep slopes in even in the downtown. 
