---
title: "TITLE"
author: "AUTHOR"
description: "DESCRIPTION"
output:
  distill::distill_article:
    self_contained: false
---

```{r}
options(width = 100)
library(infer)
library(tidyverse)
library(ggplot2)
```



## Introduction
* where you introduce the research question
* hypothesis
* briefly describe why it is interesting



## Data
* how is data collected
* type of research design
* a plot that summarizes the dependent variable and interpretaton (figure 1)

| Variable     | Description                                                                                                                        |
|---------------------|---------------------------------------------------|
| `workingday` | Indicator variable for whether day is a working day. If the day is neither weekend nor holiday is 1, otherwise is 0.               |
| `weathersit` | Indicator variable for weather inclemency. 1 for sunny or cloudy, 2 for mist, 3 for light precipitation, 4 for heavy precipitation |
| `temp`       | Normalized temperature in Celsius.                                                                                                 |
| `atemp`      | Normalized feeling temperature in Celsius.                                                                                         |
| `hum`        | Normalized humidity.                                                                                                               |
| `windspeed`  | Normalized wind speed.                                                                                                             |
| `casual`     | Count of casual users.                                                                                                             |
| `registered` | Count of registered users.                                                                                                         |
| `cnt`        | Count of total rental bikes including both casual and registered.                                                                  |

```{r}
df <- read.csv("day.csv")
df <- df[,8:16]

dist_cnt <- df |>
  ggplot(aes(x = cnt)) +
  geom_histogram() +
  labs(title = "Figure 1: Distribution of CNT",
       x = "Count of CNT",
       y = "Count")
dist_cnt
```



## Result
* figure 2: one bivariate regression (showing the relationship between just the predictor you are most interested in and your outcome)
* one multivariate regression (where you control for a couple of confounders)
* separate plots of the main relationship of interest (figure 3, 4, 5)
* a summary and discussion of results in substantive context
* interpret (in plain English) the main coefficient of interest in your regression, comment on the statistical significance of the estimated coefficient, and say whether or not you believe the coefficient to represent a causal effect

```{r}
reg_main <- lm (cnt ~ weathersit, data = df)
summary(reg_main)

df |>
  ggplot(aes(x = weathersit, y = cnt)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Figure 2: Regression of CNT on Weather Inclemency",
       x = "Weather Inclemency",
       y = "CNT")
```

```{r}
reg_all <- lm(cnt ~ workingday + weathersit + temp + atemp + hum + windspeed, data = df)
summary(reg_all)
```

```{r}
df |>
  ggplot(aes(x = atemp, y = cnt)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Figure 3: Regression of CNT on Feeling Temperature",
       x = "Normalized feeling temperature (Celsius)",
       y = "CNT")

df |>
  ggplot(aes(x = hum, y = cnt)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Figure 4: Regression of CNT on Humidity",
       x = "Normalized Humidity",
       y = "CNT")

df |>
  ggplot(aes(x = windspeed, y = cnt)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Figure 5: Regression of CNT on Wind Speed",
       x = "Normalized Wind Speed",
       y = "CNT")
```



## Conclusion
* a recap of results
* discussion of limitations of the study
* how to improve the study in the future (a paragraph)
