---
title: "TITLE"
author: "AUTHOR"
description: "DESCRIPTION"
output:
  distill::distill_article:
    self_contained: false
---

```{r}
options(width = 100)
library(infer)
library(tidyverse)
library(ggplot2)
library(ggcorrplot)
library(mice)
```

## Introduction

## Data

```{r}
df <- read_csv("day.csv")
df
```

| Variable     | Description                                                                                                                        |
|-------------------|-----------------------------------------------------|
| `workingday` | Indicator variable for whether day is a working day. If the day is neither weekend nor holiday is 1, otherwise is 0.               |
| `weathersit` | Indicator variable for weather of the day. 1 for sunny or cloudy, 2 for mist, 3 for light precipitation, 4 for heavy precipitation |
| `temp`       | Normalized temperature in Celsius.                                                                                                 |
| `atemp`      | Normalized feeling temperature in Celsius.                                                                                         |
| `hum`        | Normalized humidity.                                                                                                               |
| `windspeed`  | Normalized wind speed.                                                                                                             |
| `casual`     | Count of casual users.                                                                                                             |
| `registered` | Count of registered users.                                                                                                         |
| `cnt`        | Count of total rental bikes including both casual and registered.                                                                  |

```{r}
df |>
  ggplot(aes(x = temp, y = cnt)) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE) +
  labs(x = "Normalized temperature (Celsius)", 
       y = "Count of total rental bikes")
```

```{r}
dist_temp <- df |>
  ggplot(aes(x = temp)) +
  geom_histogram() +
  labs(title = "Distribution of Temperature",
       x = "Normalized temperature (Celsius)")
dist_temp

dist_hum <- df |>
  ggplot(aes(x = hum)) +
  geom_histogram() +
  labs(title = "Distribution of Humidity",
       x = "Normalized humidity")
dist_hum

dist_casual <- df |>
  ggplot(aes(x = casual)) +
  geom_histogram() +
  labs(title = "Distribution of Count of Casual Users",
       x = "Count of casual users")
dist_casual
```

```{r}
dist_cnt <- df |>
  ggplot(aes(x = cnt)) +
  geom_histogram() +
  labs(title = "Distribution of Count of Total Rental Bikes",
       x = "Count of total rental bikes")
dist_cnt
```

## Result

```{r}
reg_cnt <- lm(cnt ~ workingday + weathersit + temp + atemp + hum + windspeed + casual + registered, data = df)

modelsummary::modelsummary(reg_cnt,
                           statistic = c("s.e. = {std.error}",
                                         "p = {p.value}"),
                           gof_map = c("nobs", "r.squared", "adj.r.squared"))
```

## Conclusion
