---
title: "TITLE"
author: "AUTHOR"
description: "DESCRIPTION"
output:
  distill::distill_article:
    self_contained: false
---

```{r}
options(width = 100)
library(infer)
library(tidyverse)
library(ggplot2)
library(dplyr)
```



## Introduction
* where you introduce the research question
* hypothesis
* briefly describe why it is interesting



## Data
This dataset is based on the system data of a bike sharing company, Washington, D.C.'s Capital Bikeshare and weather information from http://www.freemeteo.com, showing the daily count of rental bikes between years 2011 and 2012 in the system with the corresponding weather conditions.

The following table shows the variables excerpted from the raw dataset. It has 6 independent variables, including `workingday`, `weathersit`, `temp`, `atemp`, `hum`, and `windspeed` and 1 dependent variable, `cnt`. Precisely, the `cnt` is a discrete variable of the total number of bikes borrowed by both casual and registered users. The `workingday` is a dichotomous variable; if the day is neither weekend nor holiday is 1, otherwise is 0. The `weathersit` is a categorical variable coded from 1 to 4 in accordance with the weather inclemency. The `temp` is the normalized temperature in Celsius whose values are derived via $\frac{t - t_{min}}{t_{max} - t_{min}}$. The `atemp` is the normalized feeling temperature in Celsius whose values are derived via $\frac{t - t_{min}}{t_{max} - t_{min}}$. The `hum` is the normalized humidity where the values are divided to 100. The `windspeed` is the normalized wind speed where the values are divided to 67.

This is a cross-sectional study that runs a bivariate regression of `cnt` on `weathersit` to explores the relationship between the count of rental bikes and weather inclemency and then a multivariate regression of `cnt` on all independent variables to control the confounders.

| Variable     | Description                                                                                                                        |
|---------------------|---------------------------------------------------|
| `workingday` | Indicator variable for whether day is a working day (1) or not (0). |
| `weathersit` | Indicator variable for weather inclemency, segmented as sunny or cloudy (1), mist (2), light precipitation (3), and heavy precipitation (4). |
| `temp`       | Normalized temperature in Celsius.                                                                                                 |
| `atemp`      | Normalized feeling temperature in Celsius.                                                                                         |
| `hum`        | Normalized humidity.                                                                                                               |
| `windspeed`  | Normalized wind speed.                                                                                                             |
| `cnt`        | Count of total rental bikes.                                                                  |

According to the plot (Figure 1), the distribution of the dependent variable, the daily count of rental bikes, looks approximately multimodal with one primary peak at the center of the curve around 4500 and two smaller peaks around 2000 and 7000, respectively.

```{r}
df_raw <- read.csv("day.csv")
df <- df_raw[, c(8, 9, 10, 11, 12, 13, 16)]

dist_cnt <- df |>
  ggplot(aes(x = cnt)) +
  geom_histogram() +
  labs(title = "Figure 1: Distribution of CNT",
       x = "Count of CNT",
       y = "Count")
dist_cnt
```



## Result
In the bivariate regression, the coefficient of `weathersit` is -1057.3, which means that a one-point increase in weather inclemency is associated with a decrease in count of total rental bikes of 1057.3 on average. According to the boxplot (Figure 2), as the lower quartile, median, and upper quartile get lower when the weather gets more inclement, the count of total rental bikes tends to decrease when the weather inclemency increases.

```{r}
reg_main <- lm (cnt ~ weathersit, data = df)
summary(reg_main)

df |>
  mutate(
    weather = case_when(
      weathersit == 1 ~ "Sunny or Cloudy",
      weathersit == 2 ~ "Mist",
      weathersit == 3 ~ "Light Precipitation",
      weathersit == 4 ~ "Heavy Precipitation"
    )
  ) |>
  ggplot(aes(x = weather, y = cnt)) +
  geom_boxplot() +
  labs(title = "Figure 2: Relationship Between CNT and Weather",
       x = "Weather",
       y = "CNT")
```

In the multivariate regression, the p-values of `weathersit`, `atemp`, `hum`, and `windspeed` are smaller than 0.1, so their coefficient are statistically significant at the 0.1 level.

Precisely, the coefficient of `weathersit` is -483.3, meaning that holding other variables at a fixed value, a one-point increase in weather inclemency is associated with a decrease in count of total rental bikes of 483.3 on average. The coefficient of `atemp` is 4483.3, meaning that holding other variables at a fixed value, a one-point increase in normalized feeling temperature is associated with an increase in count of total rental bikes of 4483.3 on average. The coefficient of `hum` is -1936.8, meaning that holding other variables at a fixed value, a one-point increase in normalized humidity is associated with a decrease in count of total rental bikes of 1936.8 on average. The coefficient of `windspeed` is -3963.3, meaning that holding other variables at a fixed value, a one-point increase in normalized wind speed is associated with a decrease in count of total rental bikes of 3963.3 on average.

Also, there is a change in the coefficient of `weathersit` in the two models. The size of the estimated negative effect of `weathersit` has on `cnt` decreases once `atemp`, `hum`, and `windspeed` are controlled. In other words, some of the effect weather inclemency has on the count of total rental bikes, detected in the bivariate regression, is caused by the confounding variables, which in this case are feeling temperature, humidity, and wind speed. This is intuitive because the weather inclemency index are categorized in accordance with types of weather and the different types of weather are characterized by different level of those parameters; for example, an inclement rainy day has higher level of humidity and an inclement snowy day has lower feeling temperature.

It is plausible to interpret the effect of weather inclemency causally, as its confounders can be controlled.

```{r}
reg_all <- lm(cnt ~ workingday + weathersit + temp + atemp + hum + windspeed, data = df)
summary(reg_all)
```

```{r}
df |>
  ggplot(aes(x = atemp, y = cnt)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Figure 3: Regression of CNT on Feeling Temperature",
       x = "Normalized feeling temperature",
       y = "CNT")

df |>
  ggplot(aes(x = hum, y = cnt)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Figure 4: Regression of CNT on Humidity",
       x = "Normalized Humidity",
       y = "CNT")

df |>
  ggplot(aes(x = windspeed, y = cnt)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Figure 5: Regression of CNT on Wind Speed",
       x = "Normalized Wind Speed",
       y = "CNT")
```



## Conclusion
* a recap of results
* discussion of limitations of the study
* how to improve the study in the future (a paragraph)
